### 2023-11-21 main.tex
^^

\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series we have that  

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]

@@

We rewrite the above equation as

@@

	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]

@@

We observe that, for all $x\in \{1,\ldots,L\}$,
	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
Therefore we have that

@@

We introduce the summation indices $c_{x}\in \{\delta_{\tau_{x},N},1\}$ for all $x\in \{1,\ldots,L\}$.
and we observe that 
	&\sum_{\sigma_{x}=1}^{N}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
	=
	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
\end{align} Then, we replace the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$ as 

@@

Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.

@@

\begin{remark} By changeing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

	\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x}-\delta_{\tau_{x},N})}\dt

@@

	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-c_{j})\right)

@@

We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it in a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by

@@

 where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$. Equation \eqref{interpretation-PsiP} will be useful in the exact formula for the steady state. Given $\bm{\tau}$ as before, we can introduce $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ the number of occupied sites. Then we denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle is present. Finally, we call 

@@

In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from the ground state $|\Psi^{'}\rangle$ found in \eqref{ABS_1}.

@@

\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]

@@

@@

@@

		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $i_{q_{1}},\ldots,i_{q_{k}}$. In the last equality we have summed over all possible $\sigma\in \Omega^{'}$. Finally, using equation \eqref{interpretation-PsiP}, the result follows. 

@@

\paragraph{$|\Psi^{''}\rangle$ for SSEP} When we stop distinguishing colours we have that 

@@

\paragraph{$|\Psi^{'}\rangle$ for SSEP} In the colour-blind case, the ground state of $H^{'}$ reads

@@

\textbf{Proof}: the proof follows from \eqref{implicit-steadyState} and \eqref{PsiI-N2}. 

>>>>

\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Using the exponential series we have that  

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]

@@

We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\tau_{x},\sigma_{x}\in \{1,\ldots,N\}$, we have 
	\delta_{\tau_{x},\sigma_{x}}+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})=&\delta_{\tau_{x},\sigma_{x}}(\delta_{\sigma_{x},N}+1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
	=&\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})

@@

%	\Psi^{'}(\bm{\tau})%=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} (1-\delta_{\tau_x,N})\delta_{N,\sigma_x}\right]\nonumber\\
%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
%	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
%	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\
%	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\

@@

Therefore we can replace $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$ with $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ in \eqref{ABS_intermediate}. 
%	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
%	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
As a consequence we rewrite \eqref{ABS_intermediate} as 

@@

For all $x\in \{1,\ldots,L\}$ we introduce the summation index $c_{x}\in \{\delta_{\tau_{x},N},1\}$ and we have that 
	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)
Then, by replacing the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$, we obtain  

@@

Considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, \eqref{ABS-vect} follows.

@@

\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(L+2-\sum_{x=1}^{L}c^{'}_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}\dt

@@

	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)

@@

We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by

@@

 where the above average is taken with respect to the non-equilibrium steady state of the process $\bm{\sigma}$. Equation \eqref{interpretation-PsiP} will be useful in Remark \ref{remark-NESS-invertingS1}. Given $\bm{\tau}$ as before, we can introduce the number of occupied sites $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$. We denote by $x_{1},\ldots,x_{\ell}$, such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,\ell-1\}$, the coordinates where a particle of any (non-empty) type is present. Finally, we call 

@@

In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula follows from Corollary \ref{Corollary-NESS-ABS}.

@@

\begin{remark}[Obtaining the steady state from the similarity $S_{1}$]\label{remark-NESS-invertingS1}

@@

			\begin{align}\label{implicit-PSI-PSIp}

@@

				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\

@@

		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$. In the last equality we have summed over all possible $\sigma\in \Omega^{'}$. Finally, using equation \eqref{interpretation-PsiP}, the result follows. 

@@

\paragraph{$|\Psi^{''}\rangle$ for SSEP} The ground state of $H^{''}$ is 

@@

\paragraph{$|\Psi^{'}\rangle$ for SSEP} The ground state of $H^{'}$ reads

@@

\textbf{Proof}: the proof follows from \eqref{implicit-PSI-PSIp} and \eqref{PsiI-N2}. 
